Information Disclosure Concerns in The Age of Wearable Computing

### 2016-02-02 USEC2016-camera-ready/camera-ready.tex
Fixed various typos and grammatical errors, used correct reference format

\begin{abstract}
\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential information disclosure risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify which users find most concerning if disclosed. Our study relatively ranks a potential data capture scenarios enabled by wearables and investigates the impact of the recipient of the data on the perceived risk of data disclosure. We conclude with a brief survey of users' perception of  general risks associated with wearable devices, which includes factors such as safety, changes in social behaviors, and impact on fashion. To our knowledge, this is the largest user-based experiment concerning information disclosure regarding wearables. We hope that this work will aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}

@@

Wearables are a \$700 million, growing industry~\cite{cmo}. With 20\% of the population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, ubiquitous computing is becoming a reality. This trend will continue, as 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.

Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to a virtual-object filled augmented reality. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Although wearable devices are still in their infancy, we have already seen manifestations of these risks. Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users ~\cite{1_russell_2014, 16_gross_2014}.

Wearables' sensor capabilities, continuous access, and ubiquitous presence will result in a firehose of familiar and unfamiliar types of data, at a rate which will likely dwarf the amount of data currently captured by smartphones. Bystanders of wearable devices have already expressed interest in such communication, desiring notification before data about them is captured~\cite{denning2014situ}. However, subjecting people to increased notifications is not a sound option, as it has shown to lead to negative effects, such as frustration and habituation~\cite{bohme2011security}. An understanding of user concerns may allow for targeted and effective communication with the user, inform design of future permission systems, or provide insight for access control mechanisms.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We give a relative ranking of 72 potential capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
\item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient. 
\item We sketch a landscape of users' self-reported general risks regarding wearable devices and analyze responses using logistic regression models. 
\end{itemize}

\section{Methodology}
We designed a survey for our IRB-approved study to capture the general public's perception of information disclosure risks associated with wearables. To determine the most concerning data disclosure scenarios, we asked them to rate their level of concern for a 6 of scenarios from a list of 72 possible scenarios. This was intended to elicit their perception of the severity and impact of the risk. The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}. To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we asked our participants an open-ended question.

To obtain a representative list of scenarios, 4 researchers examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks. These devices' capabilities and requested permissions were the basis for the list of possible data capture scenario questions used in this study, which we feel will be representative of what users are likely to encounter today. For a scenario to be included in this study, the scenario was required to be understandable to a user, possible to happen with today's wearable devices, and capture unique information not in other scenarios.

@@

To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios. The average survey completion time was 11.5 minutes, which includes four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables. See Appendix \ref{sec:noquestions} for details.\\

\noindent {\bfseries Comprehension Questions}
The survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks. Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios on a fictitious wearable. We highlighted the capabilities of this device and described use cases:\\

@@

To guarantee that participants had understood its capabilities, we asked two multiple-choice comprehension questions and filtered out responses from participants who did not answer both questions correctly.\\

@@

\noindent {\bfseries Additional Questions}
The exit portion of the survey collected demographics (age, gender, and education) and wearable device ownership so we could control for prior exposure. An open-ended question the most likely risks associated with wearable devices was included to capture user concerns more broadly. To avoid biasing the open-ended question, we asked before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which was included so we could control for participants' general privacy attitudes. However, we realize that we asked this open-ended question after exposing participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks. We talk about this more in Section 4.

\subsection{Focus Group}
We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue. The focus group participants took the survey, gave feedback on the format and the content, and noted any confusions. The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional information disclosure scenarios. The Craigslist-recruited participants received \$30 in cash for their time. Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 ($\mu = 36.1$, $\sigma = 15.3$).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.

@@

\section{Results}
We had at least 141 responses per data type, 2,779 per recipient, and 35 responses per each unique data type/recipient combination. In this section, we present participants' responses to the various data disclosure scenarios and discuss various factors contributed to their risk perceptions. We conclude the section with self-reported general wearables concerns.\\

\noindent {\bfseries Data Type}
Based on our statistical models (later reported in Section \ref{sec:regression}), we observe that the largest effect on participants' VURs stemmed from the data being shared, rather than  with whom the data is shared. The most and least concerning data types are listed in Table \ref{top10-table}.

Participants were most concerned about photos and videos, especially if they contained embarrassing content, personal content, nudity, financial information, or information that can be used to impersonate someone (e.g., usernames/passwords for websites). As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and are almost unanimously considered to be concerning.

@@

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test, given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were not as significant. Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & \textless0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & \textless0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & \textless0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & \textless0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & \textless0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & \textless0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient-chi}
\end{center}
\end{table}

\noindent {\bfseries Open-ended Concerns}
We captured participants' reactions to wearable devices as a whole by asking the following open-ended question:

@@

Participants were asked to write in a blank box, with no particular suggestion on what to talk about or a character limit to their responses. Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details which responses were categorized in a coding label. Note that participants were especially concerned with privacy and security. Many answers mention scenarios not included in the study, but prior exposure to our questions may have heightened sensitivity to information disclosure risks. \\

@@

Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EMF waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\

@@

Interestingly, a modest amount of participants were also concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\

@@

The landscape of users' perceived risks associated with wearables is broad, encompassing concepts outside of privacy and security. We hope that this frames our research to be just one aspect of risks associated with wearables, and motivates researchers to investigate these other risks. \\

@@

While these models illustrate the relative weights that users place on information when determining a scenario as truly upsetting, one shortcoming of this approach is its generalizability: the data predictor is categorical and limited to the data that we specifically chose for this study. To make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the type of data (e.g., video, audio, etc.) and the type of risk it presents. Two researchers agreed on a codebook and independently coded each of the 72 data types.\\

The data types fell into these six categories:\\

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information\\
\end{enumerate}

While the first three categories are self-explanatory, the latter three categories are based on user characteristics. We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits. \\

The risks for data types fell into these five categories:\\

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} the loss of money or property.
\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing).
\item {\bf Medical:} the disclosure of medical information.
\item {\bf Physical:} physical harm to the user.
\item {\bf Relationships:} damage to the user's inter-personal relationships.\\
\end{enumerate}

@@

\noindent {\bfseries Limitations}
One of the limitations of our experiment is that our participants might not have knowledge or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable. Because of this, our participants may be over or underestimating the risk, stemming from an unawareness of what can be inferred from the data, not having clear relations of new technology with respect to familiar ones, and a higher likelihood of being influenced by reports of recent events.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  Biometrics were generally not a concern for our participants, although there are security and privacy implications~\cite{prabhakar2003biometric}. Our participants also did not differentiate between the benefits and risks of various new capabilities.

@@

Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}. At the same time, our results do reflect actual perceptions of wearable devices and the associated information disclosure scenarios. This is an unavoidable, yet important distinction to make with of studies of this nature: our primary goal was to examine perceptions and acceptance so that future systems can be designed with these in mind. We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over {\it post hoc} approaches (or ignoring user concerns altogether).

Although we presented our participants with a prompt illustrating all the benefits of a wearable device, the questions we asked isolated the risk from the benefits of sharing data with a particular recipient. We sacrificed context due to the complexity of the question necessary for the participant to answer correctly. Users are willing to tolerate risks if there is enough benefit associated with that risk. We do believe that since all of our questions were out of context, our study does represent what data people ambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\

@@

We find that although people have opinions on applications which are familiar, users are still unfamiliar with particular data types or capabilities. We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work broadly in contextual and user-input-independent permission models and access control schemes.

@@

Our study is limited to owners of general consumer wearable devices. Denning {\it et al.}\ study the effect of wearables on bystanders, to find that bystanders have a range of indifferent to negative reactions which depend on the how acceptable users find the recording to be. Nasir {\it et al.}\ specifically explore medical wearables, to find that perceived risk determines physician and user acceptance of wearable health technologies.

@@

\noindent {\bfseries Ubiquitous Sensing} We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique problems present in terms for law and policy~\cite{roesner2014augmented}. Privacy preservation research in this age of ubiquitous sensing include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}. Our work aims to guide these efforts with an insight into user acceptance of common information risks. \\

\noindent {\bfseries Lessons from Smartphones} Not long ago, smartphones revolutionized applications' access to  data. While this tends to benefit users, they do not think of the privacy implications. There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}, which are applicable to wearables.

@@

 Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric information disclosure concerns int he age of wearable computing. We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients. Our open-ended responses show that privacy and security are at the top of user's overall concerns. While wearables are still in their infancy, perceptions of situations and capabilities are likely to change rapidly with advancements and increased exposure. Our examination of possible data concerns agree with previous studies of smartphone users that found that video capture and financial data are the most sensitive data types, and least acceptable to be disclosed without user consent. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous. We also found that users' self-reported privacy preferences are correlated with how they may react, even with respect to situations that they are unfamiliar with. Our results may be used by system designers to create permissions and access control mechanisms that do not directly depend on users' inputs. We hope that this work has given an insight into user acceptability in information disclosure and general user concerns about wearable devices, and that this study motivates privacy and security work for wearable devices.

\bibliographystyle{abbrv}
\bibliography{bibliography.bib}

>>>>

\begin{abstract}
\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential information disclosure risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify the data disclosure scenarios that users find most concerning. Our study relatively ranks potential data capture scenarios enabled by wearables and investigates the impact of the recipient of the data on the perceived risk of data disclosure. We conclude with a brief survey of users' perception of general risks associated with wearable devices, which includes factors such as safety, changes in social behaviors, and impact on fashion. To our knowledge, this is the largest user-based experiment concerning information disclosure surrounding wearables. We hope that this work will aid in the design of future user notifications, permission management, and access control schemes for wearables.
\end{abstract}

@@

Wearables are a growing \$700 million industry~\cite{cmo}. With 20\% of the population owning at least one wearable and 10\% using it daily~\cite{WearableStatNews}, ubiquitous computing is becoming a reality. This trend will continue, as 52\% of technology consumers are aware of wearables and 33\% are likely to buy one~\cite{NPD}.

Wearable devices enable benefits ranging from a fitness-data inspired lifestyle to virtual-object filled augmented reality. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Although wearable devices are still in their infancy, we have already seen manifestations of these risks. Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, but still resulted in tech hate crimes against its users~\cite{1_russell_2014,16_gross_2014}.

Wearables' sensor capabilities, continuous access, and ubiquity will result in a firehose of familiar and unfamiliar types of data, at a rate which will likely dwarf the amount of data currently captured by smartphones. Bystanders in the proximity of wearable devices have already expressed interest in being notified before data about them is captured~\cite{denning2014situ}. However, subjecting people to increased notifications is not a sound option, as it has shown to lead to negative effects, such as frustration and habituation~\cite{bohme2011security}. An understanding of user concerns may allow for targeted and effective user communication, inform design of future permission systems, or provide insights for access control mechanisms.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item We relatively rank 72 potential capture scenarios, which were inspired from the capabilities from the most popular wearable devices on the market at the time of the study. 
\item We study 4 possible data recipients to find that the recipient of the data contributes to the magnitude of overall perceived risk, but do not find statistically significant correlated factors of risk between data and recipient. 
\item We sketch a landscape of users' self-reported general risks regarding wearable devices and analyze responses using logistic regression models. 
\end{itemize}

\section{Methodology}
We designed a survey for our IRB-approved study to capture the general public's perception of information disclosure risks associated with wearables. To determine the most concerning data disclosure scenarios, we asked participants to rate their level of concern for 6 scenarios drawn from a list of 72 possible scenarios. This was intended to elicit their perception of the severity and impact of the risk. The format of this section was based on Felt {\it et al.}'s study of user perceptions of security and privacy risks with mobile devices~\cite{Felt}. To get a qualitative, unbounded measurement of what people thought the most common risk associated with wearables are, we asked our participants an open-ended question.

To obtain a representative list of scenarios, 4 researchers examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study (August 2014), the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; and Google Glass, which can take pictures, record video, and perform a subset Internet-based tasks. These devices' capabilities and requested permissions were the basis for the list of possible data capture scenarios used in this study, which we feel will be representative of what users are likely to encounter today. For a scenario to be included in this study, the scenario was required to be understandable to a user, possible to happen with today's wearable devices, and capture unique information not in other scenarios.

@@

To reduce fatigue, we gave our participants a randomly selected subset of wearables scenarios. The average survey completion time was 11.5 minutes, which included four questions that we omitted from this paper due to lack of participants' familiarity with specific devices and a misguided attempt to directly compare smartphones and wearables. See the appendix for details.\\

\noindent {\bfseries Comprehension Questions}
Because participants might be biased to specific companies (e.g., visceral reactions to Google Glass based on popular media stories), we framed our scenarios around a fictitious wearable. The survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearables risks. We highlighted the capabilities of this device and described use cases:\\

@@

To guarantee that participants understood its capabilities, we asked two multiple-choice comprehension questions and removed participants who did not answer both correctly.\\

@@

\noindent {\bfseries Additional Questions}
The exit portion of the survey collected demographics (age, gender, and education) and wearable device ownership so we could control for prior exposure. We included an open-ended question about the most likely risks associated with wearable devices to capture user concerns more broadly. To avoid biasing the open-ended question, we asked it before concluding with the 10-question Internet Users' Information Privacy Concerns (IUIPC) index~\cite{malhotra2004internet}, which we used to control for participants' general privacy attitudes. However, we realize that we asked this open-ended question after exposing participants to a variety of wearables scenarios, which may have heightened their awareness of the possible risks. We talk about this more in Section 4.

\subsection{Focus Group}
We conducted a one-hour focus group to validate our design, gauge comprehension, and measure fatigue. The focus group participants took the survey, gave feedback on the format and the content, and noted any confusion. The focus group concluded with a discussion of possible benefits and risks of wearable devices, in order to brainstorm any additional information disclosure scenarios. The Craigslist-recruited participants received \$30 in cash for their time. Of the 13 participants, 54\% were female, and ages ranged from 18 to 64 ($\mu = 36.1$, $\sigma = 15.3$).  Education backgrounds ranged from high school to doctorate degrees, and professions included student, artist, marketer, and court psychologist.

@@

\section{Results}
We had at least 141 responses per data type, 2,779 per recipient, and 35 responses per each unique data type/recipient combination. In this section, we present participants' responses to the various data disclosure scenarios and discuss how various factors contributed to their risk perceptions. We conclude with self-reported general wearables concerns.\\

\noindent {\bfseries Data Type}
Based on our statistical models (reported later), we observed that the largest effect on participants' VURs stemmed from the data being shared, rather than with whom the data is shared. Table \ref{top10-table} lists the most and least concerning data types.

Participants were most concerned about photos and videos, especially those containing personal or embarrassing content, nudity, financial information, or information that can be used for impersonation (e.g., usernames/passwords). As seen in Table \ref{top10-table}, photos and videos accounted for five of the top ten concerns, and were almost unanimously concerning.

@@

We note that this chi-square test violates the assumption of independent observations, since participants responded to multiple scenarios with multiple recipients. But based on the randomization of treatments and large sample size, we do not believe that this significantly impacted our results. Similarly, we are unaware of a more appropriate test (beyond using mixed effects modeling), given our data format. Cochran's Q requires binary outcomes (i.e., participants would have had to answer only one question for each data recipient, preventing us from adequately controlling for data type) and a repeated measures ANOVA requires normality (our data was not normally distributed). Nonetheless, we repeated our analysis using one randomly-selected data point per participant and found that our selected test was robust to this violation. Therefore, we conclude that participants were significantly more concerned about having their data seen by a human than an application, though differences between human groups such as the public, friends, and work contacts were not as significant. Our results motivate mechanisms for data taint tracking and accidental data sharing prevention.

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & \textless0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & \textless0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & \textless0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & \textless0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & \textless0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & \textless0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Chi-square tests to examine VUR based on data recipient.}
\label{recipient-chi}
\end{center}
\end{table}

\noindent {\bfseries Open-Ended Concerns}
We asked participants the following open-ended question:

@@

Participants did not receive any additional prompts and responded using a text box that did not have a character limit. Table \ref{openresponses} shows common user concerns related to wearable devices. The appendix details the coding of responses. Note that participants were especially concerned with privacy and security; many answers mentioned scenarios not included in the study, but prior exposure to our questions may have heightened sensitivity to information disclosure risks:\\

@@

Other common concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware), long-term health effects caused from wearing the device such as cancer from EM waves (Health), and safety hazards from wearing the device, such as distractions that cause car accidents (Safety).\\

@@

Interestingly, a few participants were concerned with resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact). \\

@@

The landscape of users' perceived risks associated with wearables is broad, encompassing concepts outside of privacy and security. We therefore hope this motivates other researchers to investigate these other risks. \\

@@

While these models illustrate the relative weights that users place on information when determining whether a scenario is truly upsetting, one shortcoming is this approach's generalizability: data types are limited to what we specifically chose for this study. To make our data set more generalizable to other use cases, we coded each data type in two ways: in terms of broad descriptions of the type of data (e.g., video, audio, etc.) and the type of risk it presents. Two researchers agreed on a codebook and independently coded each of the 72 data types. The data types fell into six categories:

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Photo
\item Video
\item Audio
\item Behavioral Information
\item Biometric Information
\item Demographic Information
\end{enumerate}

While the first three categories are self-explanatory, the latter three categories are based on user characteristics. We defined {\it behavioral information} as observations about the user's activities; {\it biometric information} as measurements of the user's body; and {\it demographic information} as non-biometric information about the user's traits.

The risks for data types fell into five categories:

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item {\bf Financial:} the loss of money or property
\item {\bf Image:} the loss of control over one's self-image (e.g., publicizing something embarrassing)
\item {\bf Medical:} the disclosure of medical information
\item {\bf Physical:} physical harm to the user
\item {\bf Relationships:} damage to inter-personal relationships
\end{enumerate}

@@

\noindent {\bfseries Limitations}
One of the limitations of our experiment is that our participants might not have knowledge of or interest in wearables and their capabilities; 83\% of our participants reported that they do not own a wearable device. Because of this, our participants may be overestimating or underestimating risk due to an unawareness of what can be inferred from the data collected by these devices. Our participants may not have clear understandings of new technologies with respect to familiar ones, and may also have a higher likelihood of being influenced by reports of recent events relevant to these unfamiliar devices.\footnote{At the time of the survey, stories of exploding batteries were in the news~\cite{1_levin_2014}, which were explicitly reported as a concern in our open-ended question.}  We also noted that biometrics were generally not a concern for our participants, although they have security and privacy implications~\cite{prabhakar2003biometric}. Our participants also did not differentiate between the benefits and risks of various new capabilities made possible by wearable devices.

@@

Because of the privacy paradox, participants' stated responses may differ from how they may react to these same scenarios in real life~\cite{norberg2007privacy, jensen2005privacy}. At the same time, our results do reflect actual perceptions of wearable devices and the associated information disclosure scenarios. This is an unavoidable, yet important distinction to make with studies of this nature: our primary goal was to examine perceptions and acceptance so that future systems can be designed with these in mind. We do not expect that such systems will satisfy users in all situations, however, we believe that user-centered design will still be a vast improvement over {\it post hoc} approaches (or ignoring user concerns altogether).

Although we presented our participants with a prompt illustrating all the benefits of a wearable device, the questions we asked isolated the risk from the benefits of sharing data with a particular recipient. We sacrificed context due to the complexity of the question necessary for the participant to answer correctly. Users are willing to tolerate risks if there is enough benefit associated with that risk. We do believe that since all of our questions were out of context, our study does represent what data people unambiguously would like to be private and secure, and is accurate for measuring user perceptions of wearables.\\

@@

We find that although people have opinions on applications which are familiar, users are still unfamiliar with particular data types and capabilities. We hope our work both informs the direction for future research to secure video, audio, and other currently considered sensitive sensor input channels, but also encourages work broadly in contextual and user-input-independent permission models and access control schemes.

@@

Our study is limited to owners of general consumer wearable devices. Denning {\it et al.}\ study the effect of wearables on bystanders, to find that bystanders have a range of indifferent to negative reactions which depend on how acceptable users find the recording to be~\cite{Denning2014}. Nasir {\it et al.}\ specifically explore medical wearables, to find that perceived risk determines physician and user acceptance of wearable health technologies~\cite{nasir2015consumers}.

@@

\noindent {\bfseries Ubiquitous Sensing} We are rapidly moving towards a world of ubiquitous sensing and data capture, with ensuing privacy challenges~\cite{abowd2000charting,palen2003unpacking,camp2000internet}. Roesner {\it et al.}\ urge the community to address potential concerns for wearable devices before the technologies become widespread~\cite{roesner2014security} and explore the unique problems present in terms of law and policy~\cite{roesner2014augmented}. Privacy preservation research in this age of ubiquitous sensing include frameworks to design for privacy~\cite{bellotti1993design,camp2003designing,langheinrich2001privacy}, protocols for anonymous communication~\cite{cornelius2008anonysense}, evaluation metrics for privacy~\cite{scholtz2004toward}, and privacy models~\cite{hong2004privacy, jiang2002approximate}. Our work aims to guide these efforts with an insight into user acceptance of common information risks. \\

\noindent {\bfseries Lessons from Smartphones} Not long ago, smartphones revolutionized applications' access to  data. While this tends to benefit users, they often do not think of the privacy implications. There are still many unresolved concerns such as the opaqueness that prevents users from fully understanding how applications are using their data or rogue applications inappropriately accessing data~\cite{1_kane_2010, zhou2011taming}, which are applicable to wearables.

@@

 Our survey of 1,784 Internet users is the first large-scale study to investigate user-centric information disclosure concerns in the age of wearable computing. We contribute a comprehensive ranking of possible risks associated with wearable devices, across various recipients. Our open-ended responses show that privacy and security are at the top of users' overall concerns. While wearables are still in their infancy, perceptions of situations and capabilities are likely to change rapidly with advancements and increased exposure. Our examination of possible data concerns corroborate previous studies of smartphone users that found that video capture and financial data are the most sensitive data types, and least acceptable to be disclosed without user consent. Various systems which detect and take actions for sensitive objects in photos and videos will be critical as wearables and other devices become more ubiquitous. We also found that users' self-reported privacy preferences are correlated with how they may react, even with respect to situations that they are unfamiliar with. Our results may be used by system designers to create permissions and access control mechanisms that do not directly depend on users' inputs. We hope that this work has given an insight into user acceptability in information disclosure and general user concerns about wearable devices, and that this study motivates future privacy and security work for wearable devices.

\bibliographystyle{IEEEtran}
\bibliography{bibliography.bib}
